Presentation Title

### 2017-08-07 thesis/chapters/ch1-intro.tex
Fixes

We live in a world where technologies have become vital for our welfare and success.
The internet, for instance, gave us the ability of efficiently exchange information on a global scale.
However, in contrast to its original design, the internet and in particular the world wide web is becoming increasingly centralised.
The domain name system (root name server), certificate authorities (root CA), to name a few, carry enormous responsibilities and are a central point of failure.
The  same can be said for many other services such are online marketplaces,
cloud services, hospitality services and even our banking system.
The 2008 financial crisis is an example of the banking system making poor choices which resulted in a
decline in consumer wealth in the order of trillions~\cite{financialcrisis} and led to the European debt crisis.

@@

The primary innovations are (1) the consensus model which prevents double spending,
and (2) the incentive mechanism that encourages anyone (with adequate hardware) to participate in the network and keep it running.
The double spending problem can be seen as an inconsistency issue.
For example, $C$ has 5 units of currency in her account.
If $C$ can simultaneously claim that she transferred 5 units to $A$ but also 5 units to $B$, then the system is inconsistent.
Bitcoin and many of its derivatives (e.g. Litecoin\footnote{\url{https://litecoin.org}} and Dogecoin\footnote{\url{http://dogecoin.org}}) solve the inconsistency problem with a consensus algorithm.
The goal of the algorithm is to reach agreement on a set of valid transactions. 
This effectively eliminates inconsistencies.

In Bitcoin's case, the consensus algorithm is called \emph{proof-of-work}.
Where miners (parties that run the Bitcoin network) collect transactions and compete in solving a puzzle.
The puzzle is easy to verify but difficult to solve.
Only the miner that solves it can generate a valid block containing all the collected transactions.
The miner is also rewarded with new coins and transaction fees.
It is important to note that every block, that is the solution of the puzzle,
depends on the previous block.
Hence the name blockchain.
This property ensures malicious nodes cannot easily rewrite history if they do not have a majority of the network's computing power.
Consequently, it is unlikely for more than one blockchain to exist in the network for a long period of time.
Thus every party sees a consistent blockchain which solves the double spending problem.
% Further, due to the reward mechanism,
% people are incentivised to act as miners and keep the system running.

Bitcoin has had its ups and downs, but over it has grown into an enormous system.
Its power consumption is as high as Republic of Ireland~\cite{o2014bitcoin}.
Its market capitalisation, at the time of writing, is over 60 billion USD~\cite{bitcoinmarketcap} and growing (\Cref{fig:market-cap}).
\begin{figure}[h]
\centering
\includegraphics[width=\textwidth]{market-cap}
\caption{Market capitalisation and price of Bitcoin, graph is extracted from~\cite{bitcoinmarketcap}.}
\label{fig:market-cap}
\end{figure}
Many online marketplaces are using Bitcoin.
For example, Steam\footnote{\url{https://store.steampowered.com/}} and even Amazon\footnote{Not directly, but via \url{https://purse.io/}.}.
Due to its success, people from many different disciplines began investigating in ways to use blockchain technology.
This includes finance~\cite{finance}, health care~\cite{healthcare}, logistics~\cite{supplychain} and energy~\cite{energy}.

@@

What we have described is, in fact, the current state of Bitcoin.
Many proposals exist with the aim to make Bitcoin more scalable.
The most prominent one is Segregated Witness or SegWit~\cite{segwit}.
It moves the signature data to the end of the block and uses a variable block size up to 4 MB.
The effect is that the first 1 MB of the block is still backwards compatible, thus there is no need for a hard fork.
It also solves the transaction malleability problem~\cite{bitcoinmalleability} and paves the way for off-chain transactions via Lightning Network~\cite{lightningnetwork}.
However, some fear SegWit is not enough and wish to see a hard fork that uses ``Adjustable Blocksize Cap'' that increase the block size up to 8 MB\footnote{\url{https://www.bitcoinabc.org/}}.
The ongoing civil war resulted in a Bitcoin fork, called Bitcoin Cash\footnote{\url{https://www.bitcoincash.org/}}.
At the time of writing, it is too early to speculate how these proposals and forks may affect the scalability properties of Bitcoin.
But the conclusion that we can draw from the scalability debate is that the Bitcoin design is fundamentally not scalable,
and it is highly non-trivial to ``patch'' the problem.

In this work, we take the advice of Croman et el.~\cite{croman2016scaling} and Vukoli\'{c}~\cite{vukolic2015quest} and rethink the blockchain architecture.
Our primary insight came from observing the differences between how value transfer work in the real world and how they work in early blockchain systems.
Take a restaurant owner, for example,
most of the time the customer is honest and pays the bill.
There is no need for the customer or the restaurant owner to report the transaction to any central authority 
because both parties are happy with the transaction.
On the other hand, if the customer leaves without paying the bill,
then the restaurant owner would report the incident to some central authority, e.g. the police.
On the contrary, in blockchain systems, every transaction is effectively sent to the miners,
which can be seen as a collective authority.
This consequently leads to limited scalability because every transaction must be validated by the authority even when most of the transactions are legitimate.

Using the aforementioned insight,
we explore an alternative consensus model for blockchain systems where transactions themselves do not reach consensus,
but nevertheless verifiable at a later stage by any node in the network.
Informally, our system works as follows.
Every node stores its own blockchain and every block is one transaction.
We randomly select nodes in every round, the selected ones are called facilitators.
They reach consensus not on the individual transactions,
but on the state of every chain represented by a single digest, we call this state the checkpoint.
If a checkpoint of some node is in consensus, 
then that node can proof to any other node that it holds a set of transactions that compute (form a chain) to the checkpoint.
This immediately shows that those transactions are tamper-proof.
We call our protocol Checo, derived from \emph{che}ckpoint \emph{co}nsensus.
% TODO mention consensus and trade off?

Our main contributions are the following.
\begin{itemize}
    \item We formally introduce a blockchain system---Checo.
        It uses individual hash chains and checkpoints on every node to achieve
        horizontally scalable for the first time.
    \item We formally analyse Checo to ensure correctness as defined in our architecture.
    \item We implement Checkpoint Consensus with experiment with up to 1200 nodes,
        our results show strong evidence of horizontal scalability.
\end{itemize}

>>>>

We live in a world where technologies have become vital for our welfare and success.
The internet, for instance, gave us the ability of efficiently exchange information on a global scale.
However, in contrast to its original design, the internet and in particular the world wide web is becoming increasingly centralised.
The domain name system (root name server), certificate authorities (root CA), to name a few, carry enormous responsibilities and are a central point of failure.
The  same can be said for many other services such are online marketplaces,
cloud services and even our banking system.
The 2008 financial crisis is an example of the banking system making poor choices which resulted in a
decline in consumer wealth in the order of trillions~\cite{financialcrisis} and led to the European debt crisis.

@@

The primary innovation is the consensus mechanism which prevents double spending but also incentivises anyone (with adequate hardware) to participate and keep the network running.
The double spending problem can be seen as an inconsistency issue.
For example, $C$ has 5 units of currency in her account.
If $C$ can simultaneously claim that she transferred 5 units to $A$ but also 5 units to $B$, then the system is inconsistent.
Bitcoin and many of its derivatives (e.g. Litecoin\footnote{\url{https://litecoin.org}} and Dogecoin\footnote{\url{http://dogecoin.org}}) solve the inconsistency problem with a consensus algorithm.
The goal of the algorithm is to reach agreement on a set of valid transactions. 
This effectively eliminates inconsistencies.

In Bitcoin's case, the consensus algorithm is called \emph{proof-of-work}.
Where miners (parties that run the Bitcoin network) collect transactions and compete in solving a puzzle.
The puzzle is easy to verify but difficult to solve.
Only the miner that solves it can generate a valid block containing all the collected transactions.
The miner is also rewarded with new coins and transaction fees.
It is important to note that every block depends on the previous block.
Hence the name blockchain.
This property ensures malicious nodes cannot easily rewrite history if they do not have a majority of the network's computing power.
Consequently, it is unlikely for more than one blockchain to exist in the network for a long period of time.
Thus every party sees a consistent blockchain which solves the double spending problem.
% Further, due to the reward mechanism,
% people are incentivised to act as miners and keep the system running.

Bitcoin has had its ups and downs, but overall it has grown into an enormous system.
Its power consumption is as high as Republic of Ireland~\cite{o2014bitcoin}.
Its market capitalisation, at the time of writing, is over 60 billion USD and growing (see \Cref{fig:market-cap}).
\begin{figure}[h]
\centering
\includegraphics[width=\textwidth]{market-cap}
\caption{Market capitalisation and price of Bitcoin, graph is extracted from~\cite{bitcoinmarketcap}.}
\label{fig:market-cap}
\end{figure}
Many online marketplaces are using Bitcoin.
For example, Steam\footnote{\url{https://store.steampowered.com/}} and Amazon\footnote{Not directly, but via \url{https://purse.io/}.}.
Due to its success, people from many different disciplines began investigating in ways to use blockchain technology.
This includes finance~\cite{finance}, health care~\cite{healthcare}, logistics~\cite{supplychain} and energy~\cite{energy}.

@@

The Bitcoin community understands the issue and many proposals exist with the aim to make Bitcoin more scalable.
The most prominent one is Segregated Witness or SegWit~\cite{segwit}.
It moves the signature data to the end of the block and uses a variable block size up to 4 MB.
The effect is that the first 1 MB of the block is still backwards compatible, thus there is no need for a hard fork.
It also solves the transaction malleability problem~\cite{bitcoinmalleability} which paves the way for off-chain transactions via Lightning Network~\cite{lightningnetwork}.
However, some fear SegWit is not enough and wish to see a hard fork that uses ``Adjustable Blocksize Cap'' that increase the maximum block size even further to 8 MB~\cite{bitcoincash}.
The ongoing civil war resulted in a Bitcoin fork, called Bitcoin Cash~\cite{bitcoincasharticle}.
At the time of writing, it is too early to speculate how these proposals and forks may affect the scalability properties of Bitcoin.
But the conclusion that we can draw from the scalability debate is that the Bitcoin design is fundamentally not scalable,
and it is highly non-trivial to ``patch'' the problem.

In this work, we take the advice of Croman et el.~\cite{croman2016scaling} and Vukoli\'{c}~\cite{vukolic2015quest} and rethink the blockchain architecture.
Our primary insight came from observing the differences between how value transfer work in the real world and how they work in early blockchain systems.
Take a restaurant owner, for example,
most of the time the customer is honest and pays the bill.
There is no need for the customer or the owner to report the transaction to any central authority 
because both parties are happy with the transaction.
On the other hand, if the customer leaves without paying the bill,
then the owner would report the incident to some central authority, e.g. the police.
On the contrary, in blockchain systems, every transaction is effectively sent to the miners,
which can be seen as a collective authority.
This consequently leads to limited scalability because every transaction must be validated by the authority even when most of the transactions are legitimate.

Using the aforementioned insight,
we explore an alternative consensus model for blockchain systems where transactions themselves do not reach consensus,
but nevertheless verifiable at a later stage by any node in the network.
Informally, our system works as follows.
Every node stores its own blockchain and every block is one transaction.
We randomly select nodes in every round, the selected ones are called facilitators.
Facilitators reach consensus not on the individual transactions,
but on the state of every chain represented by a single digest, called a checkpoint block.
If a checkpoint block of some node is in consensus, 
then that node can proof to any other node that it holds a set of transactions that compute (form a chain) to the checkpoint block.
This immediately shows that those transactions are tamper-proof.
We call our protocol Checo, derived from \emph{che}ckpoint \emph{co}nsensus.
% TODO mention consensus and trade off?

Our main contributions are the following.
\begin{itemize}
    \item We formally introduce a blockchain system---Checo.
        It uses individual hash chains and checkpoints on every node to achieve
        horizontally scalable for the first time.
    \item We formally analyse Checo to ensure correctness as defined in our architecture.
    \item We provide an implementation and then experiment with up to 1200 nodes,
        our results show strong evidence of horizontal scalability.
\end{itemize}

### 2017-08-07 thesis/chapters/ch2-problem.tex
Fixes

\subsection{Early blockchain systems}
This category represents the baseline,
which are systems with a probabilistic consensus algorithm.
That is, transactions never reach consensus with a probability of 1.
The typical examples are proof-of-work based systems such as Bitcoin, Ethereum and other Altcoins.
In Bitcoin, the level of consensus of a block containing many transactions is determined by how deep it is in the Bitcoin blockchain,
also called the number of confirmation.
The probability of a block being orphaned drops exponentially as the depth increases~\cite{bitcoin}.
Nevertheless, the probability of the highest block being orphaned is non-negligible.

@@

Off-chain transaction systems are implemented using multi-signature addresses~\cite{bitcoinmultisig} and hashed time-locked Bitcoin contracts~\cite{bitcointimelock}.
In the simplest case, 
if two parties wish to make transactions,
they open a payment channel in the form of a multi-signature Bitcoin address (for two parties it would be a 2-of-2 signature address).
Each of the party must also deposit some Bitcoins in the multi-signature address,
this is called the opening transaction.
Both parties keep the channel state which is not broadcasted to the network.
The state is updated when the two parties make new transactions.
The protocol disincentivises the parties from broadcasting old channel states.
If this issue occurs, the counterparty can drain all the Bitcoins in the channel.
To close the channel, the parties simply broadcast the latest net settlement to the Bitcoin network,
this is called the closing transaction.
Effectively, only two transactions need to be broadcasted to the Bitcoin network---the opening and the closing transaction,
even if the two parties made thousands or millions of transactions in between.
The two-party scheme can be extended to a network of channels,
which allows two parties to make off-chain transactions without an open channel as long as they are connected by nodes that do.

@@

On the other hand, off-chain transactions also suffer from the problem of Bitcoin.
Proof-of-work still consumes an unreasonable amount of power.
Further, payment channels complicate user experience.
As we mentioned earlier, each node must deposit some Bitcoins into a multi-signature account.
The users must pick a suitable amount.
If the deposit is too low it would not allow large transactions.
If the deposit is too high the user is locked out of much of its Bitcoins for use outside of the channel.
In addition, the user must proactively check whether the counterparty has broadcasted an old channel state so that the user does not lose Bitcoins.
Payment channel, in theory, solves the scalability problem of early blockchain systems,
but to the best of our knowledge, its exact scalability characteristics are not investigated.

>>>>

\subsection{Early blockchain systems}
This category represents the baseline,
which are systems with a probabilistic consensus algorithm.
That is, transactions never reach consensus with a probability of 1.
The typical examples are proof-of-work based systems such as Bitcoin, Ethereum and other Altcoins.
In Bitcoin, nodes compete in solving puzzles.
The first node solves the puzzle has the privilege to create a new block.
The level of consensus of a block containing many transactions is determined by how deep it is in the Bitcoin blockchain,
also called the number of confirmation.
The probability of a block being orphaned drops exponentially as the depth increases~\cite{bitcoin}.
Nevertheless, the probability of the highest block being orphaned is non-negligible.

@@

Off-chain transaction systems are implemented using multi-signature addresses~\cite{bitcoinmultisig} and hashed time-locked Bitcoin contracts~\cite{bitcointimelock}.
In the simplest case, 
if two parties wish to make transactions,
they open a payment channel in the form of a multi-signature Bitcoin address (for two parties it would be a 2-of-2 signature address).
Each of the party must also deposit some Bitcoins in the multi-signature address,
this is called the opening transaction.
Both parties keep the channel state which is not broadcasted to the network.
The state is updated when the two parties make new transactions.
The protocol disincentivises the parties from broadcasting old channel states.
If this occurs, the counterparty can drain all the Bitcoins in the channel.
To close the channel, the parties simply broadcast the latest net settlement to the Bitcoin network,
this is called the closing transaction.
Effectively, only two transactions need to be broadcasted to the Bitcoin network---the opening and the closing transaction,
even if the two parties made thousands or millions of transactions in between.
The two-party scheme can be extended to a network of channels,
which allows two parties to make off-chain transactions without an open channel as long as they are connected by nodes that do.

@@

On the other hand, off-chain transactions also suffer from the problem of Bitcoin.
Namely, proof-of-work consumes an unreasonable amount of power.
Further, payment channels complicate user experience.
As we mentioned earlier, each node must deposit some Bitcoins into a multi-signature account.
The users must pick a suitable amount.
If the deposit is too low it would not allow large transactions.
If the deposit is too high the user is locked out of much of its Bitcoins for use outside of the channel.
In addition, the user must proactively check whether the counterparty has broadcasted an old channel state so that the user does not lose Bitcoins.
Payment channel, in theory, solves the scalability problem of early blockchain systems,
but to the best of our knowledge, its exact scalability characteristics are not investigated.

### 2017-08-07 thesis/chapters/ch3-model.tex
Fixes

The consensus and transaction protocol by themselves do not provide a mechanism to detect forks or other forms of tampering.
Thus we need a validation protocol to counteract malicious behaviour.
When a node wishes to validate one of its TX, it asks the counterparty for the \emph{agreed fragment} of the TX.
An agreed fragment of a TX block is a section of the chain beginning and ending with CP blocks that contain the TX block,
the CP blocks must also be in consensus.
Upon the counterparty's response, the node checks that the CP blocks are indeed in consensus,
the hash pointers are valid and his TX is actually in the fragment.
The TX is valid if these conditions are satisfied.
Intuitively, this works because it is hard (because a cryptographically secure hash function is second-preimage resistant)
to create a different chain that begins and ends with the same two CP blocks.

@@

Up to this point, we do not provide a mechanism to detect forks or other forms of tampering or forging.
The validation protocol aims to solve this issue.
The protocol is also a request-response protocol, just like the transaction protocol.
But before explaining the protocol itself, we first define what it means for a transaction to be valid.

\subsection{Validity definition}
A transaction can be in one of three states in terms of validity---\emph{valid}, \emph{invalid} and \emph{unknown}.
Given a fragment $F_{v, j}$, the validity of the transaction $t_{u, i}$ is captured by the function $\textsf{get\_validity}(t, F_u, F_v)$ (\Cref{alg:get-validity}).
The first four conditions (up to \Cref{line:valid-fragment}) essentially check whether the fragment is the one that the verifier needs.
If it is not, then the verifier cannot make any decision and return \emph{unknown}.
This is likely to be the case for new transactions because $\textsf{agreed\_fragment}(\cdot)$ would be $\bot$.
The next two conditions check for tampering or missing blocks, if any of these misconducts are detected, then the TX is invalid.

@@

Further, the caller of $\textsf{get\_validity}(t_{u, i}, F_{u, i}, F_{v, j})$ is not necessarily 
$u$\footnote{In practice, it often is because after completing the TX protocol the parties are incentivised to check that the counterparty ``did the right thing''.}
Any node $w$ may call $\textsf{get\_validity}(t_u{u, i}, F_{u, i}, F_{v, j})$ as long as the caller $w$ has an agreed fragment of $t_{u, i}$---$F_{u, i}$.
$F_{u, i}$ may be readily available if $w = u$ or it may be from some other \texttt{vd\_resp} message, which we describe next in the validation protocol.

@@

    % message tampering
    \If{$m \ne m' $} 
        \State \Return \emph{invalid}
    \EndIf
    \State

@@

\subsection{Validation protocol}
Our validation protocol is designed to classify transactions according to the aforementioned validity definition.
The protocol is a simple response and request protocol shown in \Cref{alg:vd-proto}.
If $u$ wishes to validate some TX with ID $txid$ and counterparty $v$, it sends $\langle \texttt{vd\_req}, txid \rangle$ to $v$.
The desired properties of the validation protocol are as follows.
\begin{definition}
\label{def:validation}
\textbf{\emph{Properties of the validation protocol}}

@@

There are a variety of approaches to do global fork detection.
First and the easiest solution is to simply ask for every agreed fragment from the one containing the genesis block up to the one that the to-be-proven TX block is in.
If the hash pointers are correct and all the CP blocks are in consensus, then the verifier can be sure that there are no forks.
We use this approach in our prior work on Implicit Consensus~\cite{implicitconsensus}.
It may sound inefficient at first, but nodes employ caching to minimise communication costs.
In our work, we call this effect ``spontaneous sharding''.

The second approach is probabilistic but with only a constant communication overhead.
For a node, observe that if all of its agreed fragment has a transaction with an honest node,
then the complete chain is effectively validated in a distributed manner.
The only way for an attacker to make a fork is to make sure that the agreed fragment containing the fork has no transactions with honest nodes.
Such malicious behaviour is prevented probabilistically using a challenge-response protocol as follows.
Suppose node $A$ wish to make a transaction with node $B$.
$A$ first sends a challenge to $B$ asking it to prove that it holds a valid agreed fragment between some consensus round specified by $A$.
If $B$ provides a correct proof, then they run the transaction protocol as usual.
If $B$ provides an invalid proof or refuses to respond,
then $A$ would refuse to make the transaction.
The probability that an honest node catches out a malicious node is 
$$p = \frac{f}{r},$$
where $f$ is the number of bad agreed fragments and $r$ is the latest round number.
If there are more nodes (say $n$) trying to make transactions with the malicious node,
then the probability that the malicious node gets caught at least once follows a binomial distribution
$$\Pr[X > 0] = \sum_{k = 1}^{n}\binom{n}{k}p^k (1 - p)^{n - k}.$$

>>>>

The consensus and transaction protocol by themselves do not provide a mechanism to detect tampering.
Thus we need a validation protocol to counteract malicious behaviour.
When a node wishes to validate one of its TX, it asks the counterparty for the \emph{agreed fragment} of the TX.
An agreed fragment of a TX block is a section of the chain beginning and ending with CP blocks that contain the TX block,
the CP blocks must also be in consensus.
Upon the counterparty's response, the node checks that the CP blocks are indeed in consensus,
the hash pointers are valid and his TX is actually in the fragment.
The TX is valid if these conditions are satisfied.
Intuitively, this works because it is hard (because a cryptographically secure hash function is second-preimage resistant)
to create a different chain that begins and ends with the same two CP blocks.

@@

Up to this point, we do not provide a mechanism to detect tampering.
The validation protocol aims to solve this issue.
The protocol is also a request-response protocol, just like the transaction protocol.
But before explaining the protocol itself, we first define what it means for a transaction to be valid.

\subsection{Validity definition}
A transaction can be in one of three states in terms of validity---\emph{valid}, \emph{invalid} and \emph{unknown}.
Given a fragment $F_{v, j}$, the validity of the TX block $t_{u, i}$ and the agreed fragment of it is captured by the function $\textsf{get\_validity}(t_{u, i}, F_{u, i}, F_{v, j})$ (\Cref{alg:get-validity}).
Note that $t_{u, i}$ and $F_{u, i}$ are assumed to be valid,
otherwise the node calling the function would have no point of reference.
This is not difficult to achieve.
Typically the caller is $u$, so it knows its own TX block and the corresponding agreed fragment.
If the caller is not $u$, it can always query for the agreed fragment that contains the transaction of interest from $u$.

\Cref{alg:get-validity} works as follows.
Before~\Cref{line:valid-fragment},
we essentially check whether the fragment is the one that the verifier needs.
If it is not, then the verifier cannot make any decision and return \emph{unknown}.
This is likely to be the case for new transactions because the result of $\textsf{agreed\_fragment}(\cdot)$ would be $\bot$.
The next two conditions check for tampering or missing blocks, if any of these misconducts are detected, then the TX is invalid.

@@

Further, the caller of $\textsf{get\_validity}(t_{u, i}, F_{u, i}, F_{v, j})$ is not necessarily 
$u$\footnote{In practice, it often is because after completing the TX protocol the parties are incentivised to check that the counterparty ``did the right thing''.}
Any node $w$ may call $\textsf{get\_validity}(t_u{u, i}, F_{u, i}, F_{v, j})$ as long as $w$ has an the necessary input parameters.
$F_{u, i}$  and $t_{u, i}$ may be readily available if $w = u$.
Otherwise, $w$ could query $u$ with the \texttt{vd\_req} message and then obtain the result from \texttt{vd\_resp}.
This is the validation protocol which we describe next.

@@

    % message tampering
    \If{$m \ne m' \vee txid \ne txid'$} 
        \State \Return \emph{invalid}
    \EndIf
    \State

@@

\subsection{Validation protocol}
Our validation protocol,
shown in~\Cref{alg:vd-proto},
is designed to classify transactions according to the aforementioned validity definition.
If $u$ wishes to validate some TX with ID $txid$ and counterparty $v$, it sends $\langle \texttt{vd\_req}, txid \rangle$ to $v$.
The desired properties of the validation protocol are as follows.
\begin{definition}
\label{def:validation}
\textbf{\emph{Properties of the validation protocol}}

@@

There are a variety of approaches to do global fork detection.
First and the easiest solution is to simply ask for the complete chain of the counterparty.
The verifier can be sure that there are no forks if the following holds.
\begin{enumerate}
    \item The hash pointers are correct.
    \item All the CP blocks are in consensus.
    \item The TX of interest is in the chian.
\end{enumerate}
We use this approach in our prior work on Implicit Consensus~\cite{implicitconsensus}.
It may sound inefficient at first, but nodes employ caching to minimise communication costs.

The second approach is probabilistic but with only a constant communication overhead over our current design.
For a node, observe that if all of its agreed fragments has a transaction with an honest node,
then the complete chain is effectively validated in a distributed manner.
The only way for an attacker to make a fork is to make sure that the agreed fragment containing the fork has no transactions with honest nodes.
Such malicious behaviour is prevented probabilistically using a challenge-response protocol as follows.
Suppose node $A$ wish to make a transaction with node $B$.
$A$ first sends a challenge to $B$ asking it to prove that it holds a valid agreed fragment between some consensus round specified by $A$.
If $B$ provides a correct proof, then they run the transaction protocol as usual.
If $B$ provides an invalid proof or refuses to respond,
then $A$ would refuse to make the transaction.
The probability that an honest node catches out a malicious node is 
$$p = \frac{f}{r},$$
where $f$ is the number of bad agreed fragments and $r$ is the latest round number.
If there are more nodes (say $n$) trying to make transactions with the malicious node,
then the probability that the malicious node gets caught at least once (denoted by the random variable $X$) follows a binomial distribution, i.e.
$$\Pr[X > 0] = \sum_{k = 1}^{n}\binom{n}{k}p^k (1 - p)^{n - k}.$$

### 2017-08-07 thesis/chapters/ch4-analysis.tex
Fixes

\subsection{Correctness of the validation protocol}
The consensus protocol (on CP blocks and facilitators) is the backbone for consensus on transactions.
In this section, we build on top of \Cref{theorem:consensus} to show that the properties except for liveness in \Cref{def:validation} can be satisfied.

\begin{theorem}
\label{theorem:validation-agreement}
% (Agreement of the validation protocol)
The validation protocol satisfies agreement and validity properties.
\end{theorem}
\begin{proof}
We proof the agreement property by contradiction.
Without loss of generality, suppose for some transaction with TX block $t$,
node $u$ decides \emph{valid} but node $v$ decides \emph{invalid}.
Then there exists a fragment $F' = \{ \dots, t', c'\}$ which $u$ received that contains a valid pair of $t$---$t'$.
There also exists a fragment $F'' = \{ \dots, t'', c''\}$ which $v$ received that does not contain or contains an invalid pair---$t''$.
In both cases, the $\textsf{get\_validity}(\cdot)$ function must have reached \Cref{line:valid-fragment}.
Due to \Cref{theorem:consensus}, we have $c' = c''$, otherwise the result would be \emph{unknown}.
Since $c' (= c'') = \langle \textsf{H}(t'), \dots \rangle$ we must have $\textsf{H}(t') = \textsf{H}(t'')$ and $t' \ne t''$ (because $t''$ is invalid).
In other words, the sender of $F''$ must be able to create some $t''$ that has the same digest as $t'$.
But this is only possible if the adversary can compute the inverse of $H(\cdot)$ with non-negligible probability.
Thus we have a contradiction and this completes the agreement proof.
Our protocol uses \Cref{alg:get-validity} which is also the validity definition,
this completes the validity proof.
\end{proof}

\Cref{theorem:validation-agreement} shows that agreement on CP blocks would lead to agreement on TX blocks when the nodes are running the validation protocol.
Like in our prior work~\cite{implicitconsensus}, we call this behaviour implicit consensus.
One of the main advantages of our scheme over running a consensus algorithm on all the transactions is that 
the transaction throughput is no longer dependent on the consensus algorithm---ACS.
This enables horizontal scalability where adding new nodes would lead to higher global transaction rate.
In addition, a convenient consequence \Cref{theorem:validation-agreement} is unforgeability.
That is, no polynomial time adversary is able to create two chains $F = \{ \dots, t, c\}$ $F' = \{ \dots, t', c\}$ with correct hash pointers and the same end of chain $c$.
% Another way to think about it is if a transaction can be forged, then it cannot be agreed.

A stronger version of the validity definition exists.
That is, if two nodes are making transactions with each other,
then the resulting transaction is always valid in addition to our current validity definition.
Under our purely asynchronous model, we cannot guarantee this stronger version.
Since the adversary can delay any message for any amount of time,
it can make sure all \texttt{tx\_req} messages are delivered in a round later than the round which the message is sent.
Effectively, the transaction pair would always be in different rounds and the validation protocol would not output \emph{valid}.
We believe in a relaxed model, i.e. a weakly synchronous model, a stronger validity definition is possible.

>>>>

\subsection{Correctness of the validation protocol}
The consensus protocol,
which ensures consensus on CP blocks and facilitators,
is the backbone for consensus on transactions.
In this section, we build on top of \Cref{theorem:consensus} to show that the properties except for liveness in \Cref{def:validation} can be satisfied.

\begin{theorem}
\label{theorem:validation-agreement}
% (Agreement of the validation protocol)
The validation protocol satisfies agreement and validity properties.
\end{theorem}
\begin{proof}
We proof the agreement property by contradiction.
From~\Cref{alg:get-validity},
we use the fact that $F_{u, i}$ and $t_{u, i}$ are valid.
Without loss of generality, suppose for some transaction with TX block $t$,
node $u$ decides \emph{valid} but node $v$ decides \emph{invalid}.
Then there exists a fragment $F' = \{ \dots, t', c'\}$ which $u$ received that contains a valid pair of $t$---$t'$.
There also exists a fragment $F'' = \{ \dots, t'', c''\}$ which $v$ received that does not contain or contains an invalid pair---$t''$.
In both cases, the $\textsf{get\_validity}(\cdot)$ function must have reached \Cref{line:valid-fragment}.
Due to \Cref{theorem:consensus}, we have $c' = c''$, otherwise the result would be \emph{unknown}.
Since $c' (= c'') = \langle \textsf{H}(t'), \dots \rangle$ we must have $\textsf{H}(t') = \textsf{H}(t'')$ and $t' \ne t''$ (because $t''$ is invalid).
In other words, the sender of $F''$ must be able to create some $t''$ that has the same digest as $t'$.
But this is only possible if the adversary can compute the inverse of $H(\cdot)$ with non-negligible probability.
Thus we have a contradiction and this completes the agreement proof.

Our protocol uses \Cref{alg:get-validity} which is also the validity definition,
so the validity property is also satisfied.
\end{proof}

\Cref{theorem:validation-agreement} shows that agreement on CP blocks would lead to agreement on TX blocks when the nodes are running the validation protocol.
Like in our prior work~\cite{implicitconsensus}, we call this behaviour implicit consensus.
One of the main advantages of our scheme over running a consensus algorithm on all the transactions is that 
the transaction throughput is no longer dependent on the consensus algorithm---ACS.
This enables horizontal scalability where adding new nodes would lead to higher global transaction rate.
In addition, a convenient consequence \Cref{theorem:validation-agreement} is unforgeability.
That is, no polynomial time adversary is able to create two chains, $F = \{ \dots, t, c\}$ and $F' = \{ \dots, t', c\}$, with correct hash pointers and the same end of chain $c$.
% Another way to think about it is if a transaction can be forged, then it cannot be agreed.

A stronger version of the validity definition exists.
That is, if two honest nodes make a transaction,
then the transaction state is always valid in addition to our current validity definition.
Under our purely asynchronous model, we cannot guarantee this stronger version.
Since the adversary can delay any message for any amount of time,
it can make sure all \texttt{tx\_req} messages are delivered in a round later than the round which the message is sent.
Effectively, the transaction pair would always be in different rounds and the validation protocol would not output \emph{valid}.
We believe in a relaxed model, i.e. a weakly synchronous model, a stronger validity definition is possible.

### 2017-08-07 thesis/chapters/ch5-implementation.tex
Fixes

\begin{figure}[tb]
  \centering
  \makebox[\linewidth][c]{%
  \begin{subfigure}[b]{0.7\textwidth}
    \includegraphics[width=\textwidth]{neighbour-fixed/consensus-communication-cost-vs-facilitators}
    \caption{Transactions are with fixed neighbours.}
    \label{fig:facilitators-comms-fixed}
  \end{subfigure}%
  \begin{subfigure}[b]{0.7\textwidth}
    \includegraphics[width=\textwidth]{neighbour-random/consensus-communication-cost-vs-facilitators}
    \caption{Transactions are with random neighbours.}
    \label{fig:facilitators-comms-random}
  \end{subfigure}
  }
  \caption{The communication cost of the consensus protocol increases polynomially with respect to the number of facilitators as expected from the ACS communication complexity.}
  \label{fig:facilitators-comms}
\end{figure}

\Cref{fig:facilitators-comms} shows the communication cost of the consensus protocol for varying numbers of facilitators.
There is strong evidence that the communication cost grows polynomially.
We expect this because of there are polynomial terms in the ACS communication complexity---$O(n^2|v| + \lambda n^3 \log n)$.
This also means that the rounds would take longer to complete and transactions would take longer to verify.
On the other hand, we get better fault tolerance.
Thus a linear increase in fault tolerance ($t$) costs a polynomial increase in communication cost.

>>>>

\begin{figure}[tb]
  \centering
  \makebox[\linewidth][c]{%
  \begin{subfigure}[b]{0.7\textwidth}
    \includegraphics[width=\textwidth]{neighbour-fixed/round-communication-cost-vs-facilitators}
    \caption{Transactions are with fixed neighbours.}
    \label{fig:facilitators-round-comms-fixed}
  \end{subfigure}%
  \begin{subfigure}[b]{0.7\textwidth}
    \includegraphics[width=\textwidth]{neighbour-random/round-communication-cost-vs-facilitators}
    \caption{Transactions are with random neighbours.}
    \label{fig:facilitators-round-comms-random}
  \end{subfigure}
  }
  \caption{The communication cost of the consensus protocol increases polynomially with respect to the number of facilitators as expected from the ACS communication complexity.}
  \label{fig:facilitators-round-comms}
\end{figure}

\Cref{fig:facilitators-round-comms} shows the communication cost of the consensus protocol for varying numbers of facilitators.
There is strong evidence that the communication cost grows polynomially.
We expect this because of there are polynomial terms in the ACS communication complexity---$O(n^2|v| + \lambda n^3 \log n)$.
This also means that the rounds would take longer to complete and transactions would take longer to verify.
On the other hand, we get better fault tolerance.
Thus a linear increase in fault tolerance ($t$) costs a polynomial increase in communication cost.
